---
title: "Lab 02 - Take a sad plot and make it better"
author: "Group Members:Liuborui Shi, Thomas Horn, Solomon Zhang and Ruth Ashadu"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
```

```{r load-data, message = FALSE}
staff <- read_csv("data/instructional-staff.csv")
```


--------


Team member 1 should pull to download updates and begins here.



### Exercise 1

The data will have 55 rows.


Team member 1 should knit, stage & commit, and push all changes to GitHub.

--------

Team member 2 should pull to download updates and begins here.

### Exercise 2

```{r staff-long-create}
staff <- read_csv("data/instructional-staff.csv")
staff_long <- staff %>%
  pivot_longer(
    cols = -faculty_type, 
    names_to = "year",
    values_to = "percentage"
    )
```


### Exercise 3

*Remove this text and add your answer here.*

```{r staff-long-inspect}
staff_long

```


Team member 2 should knit, stage & commit, and push all changes to GitHub.

--------

Team member 3 should pull to download updates and begins here.


### Exercise 4

Nothing is shown on the graph.

```{r lineplot-1}
staff_long %>%
  ggplot(aes(x = year, y = percentage, color = faculty_type)) +
  geom_line() 
```


### Exercise 5

The percentage of part-time faculty took the lead after approximately the year 1984 and gradually rises to 40% at 2011. The percentage of full-time tenured faculty and full-time tenure-track faculty began high but both fell below less than 2/3 of their original values, whereas that of full-time non-tenure-track faculty and graduate student employees showed opposite trends, while incrementing slightly over the 36-year timespan.

```{r lineplot-2}
staff_long %>%
  ggplot(aes(x = year, y = percentage, color = faculty_type, group = faculty_type)) +
  geom_line()
```


Team member 3 should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 6

*Remove this text and add your answer here.*

```{r lineplot-3}
# remove this comment and add your code here
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

Next team member should pull to download updates and continue from here.


### Exercise 7

*Remove this text and add your answer here. No code needed for this exercise!*


### Exercise 8

*Remove this text and add your answer here.*

```{r lineplot-4}
# remove this comment and add your code here
```


Current team member should knit, stage & commit, and push all changes to GitHub.

--------

All team members should pull to download all updates.


